Quantum Walks and Applications to Quantum Money

### 2025-04-02 presentation.tex
presentation updated

        \medskip
        \textbf{Approach:} Use discrete-time quantum walk framework:
        \[
        W = iS(2TT^* - 1)
        \]

@@

@@

    \begin{textblock*}{12cm}(0.5cm,1.5cm)
        \begin{itemize}
            \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$. However, this approach does not work when we use the Hartley transform. 
            \vspace{1cm}
            \item  To address this, we design an algorithm for computing $h$ that utilizes quantum walks.

@@

>>>>

        \medskip
        \textbf{Approach:} Use discrete-time quantum walk framework proposed by Andrew. M. Childs in 2009:
        \[
        W = iS(2TT^* - 1)
        \]

@@

        Proposed by Zhandry in 2023:

@@

    \begin{textblock*}{12cm}(0.5cm,1.5cm)
        \begin{itemize}
            \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$. However, this approach does not work exactly the same when we use the Hartley transform. 
            \vspace{1cm}
            \item  To extract $h$ directly, we design an algorithm for computing $h$ that utilizes quantum walks.

@@

        \footnotesize
        \begin{thebibliography}{99}

        \bibitem{aaronson2012}
        S.~Aaronson and P.~Christiano,
        \newblock \emph{Quantum Money from Hidden Subspaces},
        \newblock In Theory of Cryptography Conference, pp. 3--25, Springer, 2012. \\
        \url{https://arxiv.org/abs/1203.4740}

        \bibitem{zhandry2017}
        M.~Zhandry,
        \newblock \emph{Quantum Lightning Never Strikes the Same State Twice},
        \newblock In EUROCRYPT 2019, pp. 408--438. \\
        \url{https://arxiv.org/abs/1701.03137}

        \bibitem{childs2009}
        A.~M. Childs,
        \newblock \emph{On the Relationship Between Continuous- and Discrete-Time Quantum Walks},
        \newblock \url{https://arxiv.org/abs/0810.0312}

        \bibitem{childs2022}
        A.~M. Childs,
        \newblock \emph{Lecture Notes on Quantum Algorithms}, University of Maryland, 2022. \\
        \url{https://arxiv.org/abs/quant-ph/0012090v2}

        \bibitem{arrazola2014}
        J.~M. Arrazola and N.~Lütkenhaus,
        \newblock \emph{Quantum Walks and Graph Isomorphism},
        \newblock \url{https://arxiv.org/abs/1401.4998}

        \end{thebibliography}
